\documentclass{article}
  
 
  
  \title{HOW TO IMPROVE THE WIRELESS CONNECTION AROUND MAKERERE UNIVERSITY}
  \author{ KATUMBA HENRY  15/U/403}
  \date{18/05/2017}
  
 \begin{document}
  \maketitle
 
  
  \section{INTRODUCTION}
Makerere university known as the ivory tower has a wireless connection almost at every college with in its premisses .
Students can use this connection wherever they are to do thier researches, some use it to download academic doccuments, others use it to stream live, download videos forexample porn, music videos atc . 
Students can use their personal computers(laptops),mobile smart phones, tablets among others to accesss the wireless internet.
      	\subsection{ BACKGROUND TO THE PROBLEM}
With the increasing number of students admitted each academic year, there is a limited access to the wireless internet  connection around the university due to increased number of students accessing it hence the connections become very slow  which leads to a few students able to access the internet.
 The wireless internet is at different spots not all around the university and the general wifi hot sport around makerere(MARK AIR) does not reach every conner with in makerere.
	\subsection{ PROBLEM STATEMENT}
The university admistration should improvise installation of wifi hot spots all around the university  and also increase its band width so that it can be accessed by any student any were with in the university in order  to boost all the works done by the students using the internet.

	\subsection{AIM AND OBJECTIVES}
This project is to encourage the improvement of the wireless internet connection with in makerere university.
It shoul also increase the band width of the wireless internet connection with in the university. 
To improve all the done by students using the internet.
To make makerere university a condusive learning environment for every student whether resident or non resident.

\subsubsection{ PROJECT SCOPE}
The wireless internet connection created should reach and be accessed by all students  any were with the university premises and it should be a strong connection
	\subsubsection{ Research Significance}
	
	
 \section{ METHODOLOGY}

 Makerere university administration should ensure the provision of this strong wireless internet connection so that it can be accessible to every student of the university irrespective of their levels.
\section{REFERENCES}
School of Computing and Informatics Technology.

 

  
  \end{document} 


	